Perihelion advance of Mercury

### 2019-06-17 perihelion_advance_of_mercury.Rmd
change correction from 44 to 43

The perihelion advance of Mercury is a well-known test of general relativity.  Einstein calculated that Mercury's perihelion would advance by 44 seconds of arc per century due to general relativistic effects; here I reproduce that analysis using numerical reasoning.

@@

The orbit of Mercury has long been known to advance at a rate of about 6400'' [seconds of arc] per century.  Various classical phenomena, such as the effects of Venus, and the oblateness of the sun, account for all but 44 seconds of arc and this remaining amount puzzled astronomers for many years. According to Einstien and others, the general theory of relativity predicts an additional precession of almost exactly 44 seconds per century.  In this document I will calculate the precessional rate using numerical methods.

@@

closely agreeing with Einstein's original prediction of 44.  A more careful analysis would account for the nonzero mass of Mercury.

>>>>

The perihelion advance of Mercury is a well-known test of general relativity.  Einstein calculated that Mercury's perihelion would advance by 43 seconds of arc per century due to general relativistic effects; here I reproduce that analysis using numerical reasoning.

@@

The orbit of Mercury has long been known to advance at a rate of about 6400'' [seconds of arc] per century.  Various classical phenomena, such as the effects of Venus, and the oblateness of the sun, account for all but 43 seconds of arc and this remaining amount puzzled astronomers for many years. According to Einstien and others, the general theory of relativity predicts an additional precession of almost exactly 43 seconds per century.  In this document I will calculate the precessional rate using numerical methods.

@@

closely agreeing with Einstein's original prediction of 43.  A more careful analysis would account for the nonzero mass of Mercury.
